%-------------------------
% Resume in Latex
% Author : Julia  T{\"u}rner
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
      {#1 \vspace{-2pt}}
    }
  }


  \newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
  }


  \newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
  }


  \newcommand{\resumeEducationHeading}[6]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
  }


  \newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
  }


  \newcommand{\resumeOrganizationHeading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

  \renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

  \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
  \newcommand{\resumeItemListStart}{\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

  %-------------------------------------------
  %%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


  \begin{document}

  %---------- HEADING ----------

  \begin{center}
    \textbf{\Huge \scshape Julian T{\"u}rner} \\ \vspace{3pt}
    \small
    Josef-Scheuerl-Str. 26
    $|$
    85356 Freising
    $|$
    0178 6820769
    $|$
    tuerner.j@gmail.com
  \end{center}

  %----------- SUMMARY -----------
  \section{Summary}
  \vspace{3pt}
  \small{
    Solution-oriented software engineer with extensive experience in computer science, including enterprise grade applications. 
    Proven track record in delivering scalable software solutions and leading technology-driven business improvements. 
    Eager to leverage technical and consultative skills in a dynamic team at Google.
  }
  %----------- EDUCATION -----------

  \section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

  \resumeEducationHeading
  {FOM Hochschule f{\"u}r Oekonomie \& Management
    % \normalfont{(Admission rate: 0.09\%)}
  }{Munich, Germany}
  {B.Sc. in Computer Science;}{Sep 2021 \textbf{--} Feb 2025}
  {as part of a leisure study program}{}
  \resumeSubHeadingListEnd

  %----------- SKILLS -----------

  \section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
  \small{\item{

      \textbf{Languages:}{C\#, Typrescript, Python, C/C++} \\ \vspace{3pt}

      \textbf{Technologies:}{Windows, Linux, Desktop-Development, Web-Development, CI/CD} \\ \vspace{4pt}
  }}
  \resumeSubHeadingListEnd

  %----------- DRIVERLICENSE -----------

  \section{Driver License}
  \vspace{2pt}
  \resumeSubHeadingListStart
  \small{\item{

      \textbf{Public: }{AM, A1, A, B, BE, C1, C1E, CE, L, T} \\ \vspace{3pt}

      \textbf{Prototype: }{B0, B1, B2, E0, E1, ELF, EMA, EMM} \\ \vspace{4pt}
  }}
  \resumeSubHeadingListEnd



  %----------- EXPERIENCE -----------

  \section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Krauss-Maffei-Wegmann GmbH }{Munich, Germany}
  {Software Engineer}{Apr 2019 \textbf{--} Present, Full-time}
  \resumeItemListStart
  \resumeItem{Design and development of software for vision systems}
  \resumeItem{Architecture and development of production software for international clients}
  \resumeItem{Integration of production software into existing systems}
  \resumeItemListEnd

  \resumeSubheading
  {Ferchau Engineering GmbH}{Munich, Germany}
  {Automotive \& Software Engineer}{Sep 2017 \textbf{--} Mar 2019, Full-time}
  \resumeItemListStart
  \resumeItem{Application-oriented software development for customers}
  \resumeItem{Planning and upgrading of automotive test rigs}
  \resumeItem{Administration of vehicle management systems}
  \resumeItemListEnd

  \resumeSubheading
  {Edwork GmbH \& CO. KG }{Munich, Germany}
  {Automotive Engineer}{Jan 2017 \textbf{--} Aug 2017, Full-time}
  \resumeItemListStart
  \resumeItem{Software and hardware upgrading of automotive test rigs}
  \resumeItem{Software integration and implementation of test rigs}
  \resumeItem{Troubleshooting and maintenance of test rigs}
  \resumeItemListEnd

  % \vspace{20pt}
  \resumeSubheading
  {Volvo Group Trucks Center S{\"u}d GmbH }{Munich, Germany}
  {Automotive Engineer}{Sep 2009 \textbf{--} Dec 2016, Full-time}
  \resumeItemListStart
  \resumeItem{Execution of testing and diagnostics work on trucks}
  \resumeItem{Manufacture of custom equipment}
  \resumeItem{Emergency service planning and execution}
  \resumeItemListEnd

  \resumeSubHeadingListEnd

  %----------- PROJECTS -----------

  \section{Projects}
  \begin{itemize}[leftmargin=0.15in, label={}]

    \item[] \textbf{Battle Management System Development} \\
      Collaborated in the development of an advanced battle management system, which is currently utilized by NATO partners. My role involved contributing to critical system features, ensuring compliance with stringent security protocols, and enhancing interoperability capabilities.


    \item[] \textbf{In-Vehicle Data Integration System} \\
      Participated in the engineering of a complex interface responsible for the low-level transmission and consolidation of data across various vehicle systems, ensuring efficient intra-vehicle communication.


    \item[] \textbf{Medical Booking System Website Development} \\
      Developed a robust appointment booking website for a medical practice, which supported peak usage of 150,000 users per month, ensuring high availability and user-friendly experience.


    \item[] \textbf{Vehicle Management System Development} \\
      Engineered an internal vehicle management system to monitor bookings and vehicle status, successfully resolving issues of unequal vehicle utilization and enhancing fleet efficiency.


    \item[] \textbf{Party Planning Software Creation} \\
      Developed a centralized party planning application that organizes and manages events, which gained sponsorship from NX, demonstrating the software's innovation and market potential.


    \item[] \textbf{Custom Keyboard Assembly and Firmware Development} \\
      Constructed a custom keyboard from scratch and developed a keymap configuration using QMK firmware. The configuration was merged into the main repository, making it a candidate for the default layout.
  \end{itemize}

  %----------- CERTIFICATES -----------
  \section{Certificates}
  \hspace*{5mm} 
  \begin{tabular}{@{}p{0.45\textwidth} p{0.45\textwidth}}
    \textbf{Servicetechniker} & \textbf{Kfz-Meister Teil II} \\[0.5em]
    Kfz-Innung München-Oberbayern & Handwerkskammer für München und Oberbayern \\[0.5em]
    \textbf{KI} & \textbf{Hochvoltschulung Blitz 2} \\[0.5em]
    Carl-Cranz Gesellschaft e.V. & BMW Group \\[0.5em]
    \textbf{Grundlagen Projektmanagement} & \textbf{Design Thinking} \\[0.5em]
    ABLE Management Services GmbH & ABLE Management Services GmbH \\[0.5em]
    \textbf{Rhetorik \& Auftritt} & \textbf{Klimaanlagensachkunde nach EG 307/2008} \\[0.5em]
    ABLE Management Services GmbH & Trainmobil Trainings \\[0.5em]
    \textbf{Umgang mit pyrotechnischen Gegenständen} & \textbf{Fahrtenschreiber- \& Kontrollgeräteschulung} \\[0.5em]
    Kfz-Innung München-Oberbayern & ght GmbH \\[0.5em]
  \end{tabular}



  %----------- Community -----------

  \section{Community engagement}
  \vspace{2pt}
  \resumeSubHeadingListStart
  \small{\item{
      \textbf{StackOverflow: }{900+ Points, improved 90+ Posts, 120+ helpful Flags, 220+ Votes} \\ \vspace{3pt}
      \textbf{GitHub: }{Merged PRs: QMK Framework; Microsoft; Microsoft Docs; Docker; MahApps; NX; Qwik; Astro;} \\ \vspace{4pt}
      \textbf{Wiki: }{Creation and Self-hosting a Wiki with 180+ Pages and 70+ active Users} \\ \vspace{4pt}
      \textbf{Discord: }{Creation and administration of a Discord server (networking of students) with over 100 active users} \\ \vspace{4pt}
  }}
  \resumeSubHeadingListEnd

  %-------------------------------------------
  \end{document}
